ManuscriptPURFits

### 2024-02-21 Code/ManuscriptPURFits.Rmd

AllPURFITPlot <- AllFitsCombined |>

@@

AllPURFITPlot

@@

ggsave(file = file.path(PlotsOut, paste("AllPURFITPlot",".png",sep = "")), plot = AllPURFITPlot, device = NULL, scale = 1, height=25, width= 40, units = c("cm"),dpi = 300, limitsize = TRUE)

ggsave(file = file.path(PlotsOut, paste("AllPURFITPlot",".tiff",sep = "")), plot = AllPURFITPlot, device = NULL, scale = 1, height=25, width= 40, units = c("cm"),dpi = 300, limitsize = TRUE)

>>>>

AllStrainPurFitsPlots <- AllFitsCombined |>

@@

AllStrainPurFitsPlots

@@

ggsave(file = file.path(PlotsOut, paste("AllStrainPurFitsPlots",".png",sep = "")), plot = AllStrainPurFitsPlots, device = NULL, scale = 1, height=25, width= 40, units = c("cm"),dpi = 300, limitsize = TRUE)

ggsave(file = file.path(PlotsOut, paste("AllStrainPurFitsPlots",".tiff",sep = "")), plot = AllStrainPurFitsPlots, device = NULL, scale = 1, height=25, width= 40, units = c("cm"),dpi = 300, limitsize = TRUE)
